\begin{longtable}{lllll}
\toprule
Prompt & AdamW output & Muon all hidden output & Best routed Muon output & My observation \\
\midrule
\endfirsthead
\toprule
Prompt & AdamW output & Muon all hidden output & Best routed Muon output & My observation \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{Continued on next page} \\
\midrule
\endfoot
\bottomrule
\endlastfoot
Lily found a strange blue stone in the garden & Lily found a strange blue stone in the garden.<|endoftext|>", they could go to the bird and make a big, but it to find a little boy had a time, a time, "You have a time, there wasoftext|><|endoftext|><| had a big sun. It was a big man! S... & Lily found a strange blue stone in the garden. She and didn't see.<|endoftext|>When they had a very scared. He had a big man and tried to eat fun. He learned him to play with a sun and were very happy, Lily. I are to play with and the bi... & Lily found a strange blue stone in the garden.<|endoftext|>"We, but she loved to go to make a big, but it to find a lot of the girl, the a time. She said.<|endoftext|>Tom and were very happy, Lily. I are them to the and the big.<|endofte... & Not assessed automatically. \\
Once upon a time, there was a little robot & Once upon a time, there was a little robot. He said, "I make the door.<|endoftext|>After him. The time, it was so them with her and saw a little girl, a and she was so not a big and had a big! He went to know then, "The new mom's not can... & Once upon a time, there was a little robot. He said, "I'm very happy.<|endoftext|>After him. The little boy was so happy on the water and saw a little girl, it and she was so not a big and gave the ball. He went to the way and the the tr... & Once upon a time, there was a little robot. He said, "I'm very happy.<|endoftext|>After him, but "Can you,, Lily with my and saw a little girl, it and go again, not a big and the little She will the room. I be it was the tree.<|endoftext... & Not assessed automatically. \\
The puppy wanted to learn how to fly & The puppy wanted to learn how to fly and him.<|endoftext|>Once upon a big day, she said the little girl named Lily.<|endoftext|>When the little girl said, "Yes "You like him to play with, "I Lily was a time, but, and he was very happy. I... & The puppy wanted to learn how to fly. She was happy. She had to keep his friends, the little girl to the good and make a big other tree too.<|endoftext|>Tom and said, "I play, "That was so happy.<|endoftext|><|endoftext|><|endoftext|>Onc... & The puppy wanted to learn how to fly and said, "I not what it. They are, the little girl."<|endoftext|>The little girl could be much too too. The boy was so brave to the bird, "That was so happy.<|endoftext|>The little girl was happy, th... & Not assessed automatically. \\
\end{longtable}
